### 2020-12-04 sections/summary.tex
Update summary.tex

My doctoral research is supervised by Professor Petra Schleiter at St Hilda’s College and focuses on the stability of cabinets in Latin American presidential democracies. My research is supported by the Chilean National Agency for Research and Development. Additionally, I am interested in the political elite’s socialisation, civil services, political participation, digital media, as well as electronic and open government.
\vspace{1mm}
\end{cvparagraph}

>>>>

My doctoral research is supervised by Professor Petra Schleiter at St Hilda’s College and focuses on the stability of cabinets in Latin American presidential democracies. My research is financially supported by the Chilean National Agency for Research and Development. Additionally, I am interested in the political elite’s socialisation, civil services, and crisis management.
\vspace{1mm}
\end{cvparagraph}
